Data Anonymization for Open Science: A Case Study

### 2025-05-19 submission_materials/article.tex
revised data use and access section
move old stuff into may25 and compile

\definecolor{lightyellow}{rgb}{1.0, 1.0, 0.8}
%\sethlcolor{lightyellow}    % Use 'white' to remove the highlight
\sethlcolor{white}

@@

The public repository at\mycite{18} contains all of the anonymized data used for this paper. Note that the original pseudonymized data from which the anonymized data was derived is considered personal data and is therefore not publicly available.  \hl{Please contact Bojan Leskosek (bojan.Leskosek@fsp.uni-lj.si) or Gregor Jurak (gregor.jurak@fsp.uni-lj.si) to access the original dataset. Any data access request should state the purpose for requesting the data, describe measures how sensitive data will be protected and assurance of ethical use. Requesters need to sign a Data Use Agreement (DUA). We guarantee that reasonable requests will be honored. This data may be used for the purpose of studying anonymity, either by sharing the data or by running the anonymization software locally.}

>>>>

\definecolor{lightyellow}{rgb}{1.0, 1.0, 0.8}
\sethlcolor{lightyellow}    % Use 'white' to remove the highlight
%\sethlcolor{white}

@@

The public repository at\mycite{18} contains all of the anonymized data used for this paper. This anonymized data may be used for the purpose of studying anonymity, either by sharing the data or by running the anonymization software locally. Note that the original pseudonymized data from which the anonymized data was derived is considered personal data and is therefore not publicly available.  \hl{Please contact Bojan Leskosek (bojan.Leskosek@fsp.uni-lj.si) or Gregor Jurak (gregor.jurak@fsp.uni-lj.si) to access the original dataset. Any data access request should state the purpose for requesting the data, describe measures how sensitive data will be protected and assurance of ethical use. Requesters need to sign a Data Use Agreement (DUA). We guarantee that reasonable requests will be honored. }
